%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/seonghoon-kim-55195915a/}{\Large Seonghoon Kim}} & Email: \href{mailto:tjdgnsqn133@gmail.com}{tjdgnsqn133@gmail.com}\\
  \href{https://www.linkedin.com/in/seonghoon-kim-55195915a/}{LinkedIn}\\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Bucketplace}{Seoul, South Korea}
      {Software Engineer}{Jan 2024 -- Present}
      \resumeItemListStart
      \resumeItem{Improve development cycle}
        {I Improved a development cycle by developing an algorithm.}
      \resumeItemListEnd

    \resumeSubheading
      {HYPERCONNECT}{Seoul, South Korea}
      {Software Engineer}{Nov 2022 -- Jan 2024}
      \resumeItemListStart
      \resumeItem{CQRS}
        {I Implemented CQRS systems for the admin system. Because the number of data are 200M, it was needed to split database systems.}
      \resumeItem{SDK}
        {I Provided techknowledge to the companies under MATCH GROUP.}
      \resumeItemListEnd

    \resumeSubheading
      {CREMA}{Seoul, South Korea}
      {Tech Lead \& Manager}{Jun 2022 -- Nov 2022}
      \resumeItemListStart
      \resumeItem{Automation widget installations}
        {I developed automation processes with my team to improve our bottleneck processes. Becuase widget installation processes were inevitable and needed much time.}
      \resumeItemListEnd
      
      \resumeSubSubheading
       {Software Engineer}{Nov 2018 - Jun 2022}
       \resumeItemListStart
       \resumeItem{Review widgets}
         {I developed a main feature of the company.}
       \resumeItem{Payment migration}
         {For revenue boost, the payment migration was needed, because there were no point and cash system. I developed a new payment system including migration to provide new payment system for a few thousands clients.}
       \resumeItem{Recommendation widgets}
         {For clients' revenue boost, recommendation widgets were needed for end-user. I developed recommendation widgets by collaborating with a data science team.}
       \resumeItemListEnd

    \resumeSubheading
      {Nurigo}{Seoul, South Korea}
      {Software Engineer}{Dec 2017 - Oct 2018}
      \resumeItemListStart
      \resumeItem{Developed all new messaging services}
        {Nurigo is a messaging service provider as SaaS. I devloped all new services with a new architecture for spike traffic}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Contributions}
  \resumeSubHeadingListStart
    \resumeSubItem{Spring Projects}
      {\href{https://github.com/pulls?q=is\%3Apr+author\%3AKSH-code+archived\%3Afalse+is\%3Aclosed+org\%3Aspring-projects+}{2 merged tasks link}}
    \resumeSubItem{Rails}
      {\href{https://github.com/pulls?q=is\%3Apr+author\%3AKSH-code+archived\%3Afalse+is\%3Aclosed+org\%3Arails}{1 merged task link}}
    \resumeSubItem{Refined Github}
      {\href{https://github.com/pulls?q=is\%3Apr+author\%3AKSH-code+archived\%3Afalse+is\%3Aclosed+org\%3Arefined-github+}{3 merged tasks link}}
    \resumeSubItem{Oj}
      {\href{https://github.com/pulls?q=is\%3Apr+author\%3AKSH-code+archived\%3Afalse+is\%3Aclosed+repo\%3Aohler55\%2Foj}{1 merged task link}}
    \resumeSubItem{Connect Mongo}
      {\href{https://github.com/pulls?q=is\%3Apr+author\%3AKSH-code+archived\%3Afalse+is\%3Aclosed+repo\%3Ajdesboeufs\%2Fconnect-mongo}{1 merged task link}}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kookmin University}{Seoul, South Korea}
      {Bachelor of Science in Computer Science; Major GPA: 3.69}{Drop-out}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Honors \& Awards}
 \resumeSubHeadingListStart
   \item{
     \textbf{Software Development Hackathon}
     \begin{itemize}
      \item{[1st prize] 15th AppJam Issued by Seoul Digital Foundation - Mar 2018}
      \item{[3rd prize]}{14th AppJam Issued by Seoul Digital Foundation - Dec 2017}
     \end{itemize}
     }
     \item{
       \textbf{Algorithm Contest}
       \begin{itemize}
        \item{[1st prize]}{1st Algorithm Contest - Issued by Semyeong Computer High School - Nov 2016}
        \item{[Speicial prize]}{3rd Algorithm Contest - Issued by Nexon - Aug 2018}
        \item{[5th prize]}{3rd Algorithm Contest - Issued by Kookmin University. Aug 2018}
      \end{itemize}
   }
     \item{
       \textbf{Software Development Contest}
       \begin{itemize}
        \item{[3rd prize]}{Smarteen App Challenge 2017 - Issued by SK techx - Nov 2017}
      \end{itemize}
   }
 \resumeSubHeadingListEnd

%--------SKILLS------------
%\section{Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, JavaScript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
